---
title: "Introduction to slurmjobs"
author: 
  - name: Nicholas J. Eagles
    affiliation:
    - Lieber Institute for Brain Development
    email: nickeagles77@gmail.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('slurmjobs')`"
vignette: >
  %\VignetteIndexEntry{Introduction to slurmjobs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```


```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
## Track time spent on making the vignette
startTime <- Sys.time()

## Bib setup
library("RefManageR")

## Write bibliography information
bib <- c(
    dplyr = citation("dplyr")[1],
    R = citation(),
    BiocStyle = citation("BiocStyle")[1],
    knitr = citation("knitr")[1],
    RefManageR = citation("RefManageR")[1],
    rmarkdown = citation("rmarkdown")[1],
    sessioninfo = citation("sessioninfo")[1],
    testthat = citation("testthat")[1],
    slurmjobs = citation("slurmjobs")[1]
)
```

# Basics

## Install `slurmjobs`

`R` is an open-source statistical environment which can be easily modified to enhance its functionality via packages. `r Biocpkg("slurmjobs")` is a `R` package available via the [Bioconductor](http://bioconductor.org) repository for packages. `R` can be installed on any operating system from [CRAN](https://cran.r-project.org/) after which you can install `r Biocpkg("slurmjobs")` by using the following commands in your `R` session:

```{r "install", eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("slurmjobs")

## Check that you have a valid Bioconductor installation
BiocManager::valid()
```

## Required knowledge

`r Biocpkg("slurmjobs")` is based on many other packages and in particular in those that have implemented the infrastructure needed for dealing with RNA-seq data (EDIT!). That is, packages like `r Biocpkg("SummarizedExperiment")` (EDIT!).

If you are asking yourself the question "Where do I start using Bioconductor?" you might be interested in [this blog post](http://lcolladotor.github.io/2014/10/16/startbioc/#.VkOKbq6rRuU).

## Asking for help

As package developers, we try to explain clearly how to use our packages and in which order to use the functions. But `R` and `Bioconductor` have a steep learning curve so it is critical to learn where to ask for help. The blog post quoted above mentions some but we would like to highlight the [Bioconductor support site](https://support.bioconductor.org/) as the main resource for getting help: remember to use the `slurmjobs` tag and check [the older posts](https://support.bioconductor.org/tag/slurmjobs/). Other alternatives are available such as creating GitHub issues and tweeting. However, please note that if you want to receive help you should adhere to the [posting guidelines](http://www.bioconductor.org/help/support/posting-guide/). It is particularly critical that you provide a small reproducible example and your session information so package developers can track down the source of the error.

## Citing `slurmjobs`

We hope that `r Biocpkg("slurmjobs")` will be useful for your research. Please use the following information to cite the package and the overall approach. Thank you!

```{r "citation"}
## Citation info
citation("slurmjobs")
```

# Quick start to using `slurmjobs`

```{r "start", message=FALSE}
library("slurmjobs")
library("dplyr")
```

Edit this as you see fit =)

Here is an example of you can cite your package inside the vignette:

* `r Biocpkg("slurmjobs")` `r Citep(bib[["slurmjobs"]])`

# Monitoring Running Jobs

The `job_info()` function provides wrappers around the `squeue` and `sstat` utilities SLURM provides for monitoring specific jobs and how busy partitions are. The general idea is to provide the information output from `squeue` into a `tibble`, while retrieving memory-utilization information that ordinarily must be retrieved manually on a job-by-job basis with `sstat -j [specific job ID]`.

Retrieve info about your currently running jobs like this:

```{r "job_info_basic", eval = FALSE}
#   Get information about your jobs (default 'user' argument) on any partition
job_df <- job_info(partition = NULL)
```

The benefit to having this data in R, now, is to be able to trivially ask summarizing questions. First, "how much memory and how many CPUs am I currently using?" Knowing this answer can help ensure fair and civil use of shared computing resources, for example on a computing cluster.

```{r "job_info_total_resources"}
job_df |>
    filter(partition == "shared") |>
    summarize(
        total_mem_req = sum(requested_mem_gb),
        total_cpus = sum(cpus)
    ) |>
    print()
```

Another use case could be to get a quick idea of the maximum memory required among all running tasks in an array job, for example for a script where you'd like to tune the requested memory to be as low as necessary to complete all tasks. [TODO: really this use case makes more sense only for completed jobs]

```{r "job_info_max_memory"}
job_df |>
    #   Grab only array jobs
    filter(!is.na(array_task_id)) |>
    #   Now for each unique array job, find the highest peak memory reached
    #   across tasks
    group_by(job_id) |>
    summarize(max_peak_mem = max(max_vmem_gb)) |>
    print()
```

# Reproducibility

The `r Biocpkg("slurmjobs")` package `r Citep(bib[["slurmjobs"]])` was made possible thanks to:

* R `r Citep(bib[["R"]])`
* `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
* `r CRANpkg("dplyr")` `r Citep(bib[["dplyr"]])`
* `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])`
* `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`
* `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])`
* `r CRANpkg("sessioninfo")` `r Citep(bib[["sessioninfo"]])`
* `r CRANpkg("testthat")` `r Citep(bib[["testthat"]])`

This package was developed using `r BiocStyle::Biocpkg("biocthis")`.


Code for creating the vignette

```{r createVignette, eval=FALSE}
## Create the vignette
library("rmarkdown")
system.time(render("slurmjobs.Rmd", "BiocStyle::html_document"))

## Extract the R code
library("knitr")
knit("slurmjobs.Rmd", tangle = TRUE)
```

Date the vignette was generated.

```{r reproduce1, echo=FALSE}
## Date the vignette was generated
Sys.time()
```

Wallclock time spent generating the vignette.

```{r reproduce2, echo=FALSE}
## Processing time in seconds
totalTime <- diff(c(startTime, Sys.time()))
round(totalTime, digits = 3)
```

`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```



# Bibliography

This vignette was generated using `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
with `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])` and `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])` running behind the scenes.

Citations made with `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`.

```{r vignetteBiblio, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
## Print bibliography
PrintBibliography(bib, .opts = list(hyperlink = "to.doc", style = "html"))
```
